Post-Disturbance Tree Community Trajectories in a Neotropical Forest

### 2018-06-13 WholePlotTrajectories.Rmd
relecture

A combination of taxonomic and functional approaches are essential to fully assess communities response to disturbance and differences in their respective trajectories are insightful of underlying mechanisms [@Lohbeck2015;@Guariguata2001].
Although taxonomic and functional diversity are complementary and sometimes decoupled, they are combined in the measure of communities functional redundancy that quantifies the amount of shared trait values among species [@Carmona2016].
Functional redundancy is determinant of communities resilience as high redundancy, like in highly diverse tropical forests [@Bellwood2006], mitigates the impacts of species removal on ecosystem functioning [@Trenbath1999; @Elmqvist2003; @Diaz2005].

>>>>

A combination of taxonomic and functional approaches are essential to fully assess communities response to disturbance and the differences in their trajectories are insightful of assembly processes [@Lohbeck2015;@Guariguata2001].
The decoupling between functional and taxonomic trajectories is assessed through communities functional redundancy that quantifies the amount of shared trait values among species [@Carmona2016].
Functional redundancy, which is high in the very diverse tropical forests [@Bellwood2006], mitigates the impacts of species removal on ecosystem functioning [@Trenbath1999; @Elmqvist2003; @Diaz2005] and thus determines communities resilience. 
High functional redundancy besides increases the functional overlap among species, increasing their similarity, and would foster neutral stochastic processes [@Gravel2006].
